---
title: "WiSTEM and WiENG 2023 - 2024"
subtitle: "Student Entry Form (Pre / Post Analyses)"
format:
  html:
    toc: true
    embed-resources: true
    echo: false
    link-external-newwindow: true
execute:
  warning: false
  message: false
from: markdown+emoji  
editor: 
  markdown: 
    wrap: 72
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: load-packages

library(tidyverse)
library(patchwork)
library(readr)
library(kableExtra)

set.seed(1968)
```

```{r}
#| label: load-data-sets

# Data Sets 
entry_form_data <- read_csv(file = "data/processed/wistem_2324_entry_form_processed.csv")
pre_entry_form_data <- read_csv(file = "data/processed/wistem_2324_pre_entry_form_processed.csv")
post_entry_form_data <- read_csv(file = "data/processed/wistem_2324_post_entry_form_processed.csv")

# Leveling
entry_form_data$work_hard <- factor(entry_form_data$work_hard, levels = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))
entry_form_data$knowledge <- factor(entry_form_data$knowledge, levels = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))
entry_form_data$courses <- factor(entry_form_data$courses, levels = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))
entry_form_data$succesful <- factor(entry_form_data$succesful, levels = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))
entry_form_data$important <- factor(entry_form_data$important, levels = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))
entry_form_data$member <- factor(entry_form_data$member, levels = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))
entry_form_data$career <- factor(entry_form_data$career, levels = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))
entry_form_data$identity <- factor(entry_form_data$identity, levels = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))
entry_form_data$meaningful <- factor(entry_form_data$meaningful, levels = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))
entry_form_data$everyday <- factor(entry_form_data$everyday, levels = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))

# Future Color Reference
colors <- c("#B477FF", "#7000B0") # called in later graphs for simplicity
```

# Background

**WiSTEM:** In total, there were 15 overall WiSTEM meetings held throughout the 2023-2024 academic school year. There were 14 meetings with attendance data and 14 meetings with exit slip data (January 18th, 2024 is missing). 

**WiENG:** In total, there were 29 overall WiENG meetings held throughout the 2023-2024 academic school year. There were 26 meetings with attendance data and 23 meetings with exit slip data. Some of these overlap in missing both attendance and exit slip data.

**Distribution:** As can be seen in the table below, there were a total of 70 student forms obtained for the Pre-Test while there were 93 student forms obtained for the Post-Test. There is a large discrepancy of 23 more forms being filled out by the end of the year, but the general trend can still be identified. These forms were either filled out during the original WiSTEM meetings (where a majority of them were) while some were filled out during some WiENG meetings. 
```{r}
#| label: background

entry_form_data %>%
  count(survey_type) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100
  ) %>%
  arrange(desc(n)) %>%
  rename(
    `Number of Forms` = n, 
    `Survey Type` = survey_type, 
    Proportion = proportion, 
    Percent = percent
  ) %>%
  kbl(caption = "Distribution of Pre and Post Forms") %>%
  kable_styling()
```

# Career Analysis
## Career Amount

**Question:** List up to ten (10) STE(A)M career or job possibilities. 

```{r}
#| label: career-amount-compare

# Pre Test
pre_career_amount_plot <- ggplot(data = pre_entry_form_data, mapping = aes(x = career_amount)) + 
  geom_density() + 
  geom_rug() + 
  theme_minimal() + 
  labs(
    x = "Number of Careers", 
    y = "Density", 
    title = "Pre Test", 
    subtitle = "Unique Students", 
    caption = "Source: WiSTEM 2023-2024"
    ) + 
  theme_minimal() + 
  theme(plot.title = element_text(face = "bold"))

pre_career_amount_table <- pre_entry_form_data %>%
  count(career_amount) %>%
  mutate(
    mean = mean(career_amount), 
    max = max(career_amount), 
    min = min(career_amount), 
    std_dev = sd(career_amount),
    median = median(career_amount),
    test = "pre"
  ) %>%
  select(test, min, median, mean, std_dev, max) %>%
  head(1)

# Post Test
post_career_amount_plot <- ggplot(data = post_entry_form_data, mapping = aes(x = career_amount)) + 
  geom_density() + 
  geom_rug() + 
  theme_minimal() + 
  labs(
    x = "Number of Careers", 
    y = "Density", 
    title = "Post Test", 
    subtitle = "Unique Students", 
    caption = "Source: WiSTEM 2023-2024"
    ) + 
  theme_minimal() + 
  theme(plot.title = element_text(face = "bold"))

post_career_amount_table <- post_entry_form_data %>%
  count(career_amount) %>%
  mutate(
    mean = mean(career_amount), 
    max = max(career_amount), 
    min = min(career_amount), 
    std_dev = sd(career_amount),
    median = median(career_amount),
    test = "post"
  ) %>%
  select(test, min, median, mean, std_dev, max) %>%
  head(1)

# Compare 
## Plot
pre_career_amount_plot + post_career_amount_plot
```

::: {.callout-note icon=false collapse="true"}
## Tables for Career Amount Analysis
```{r}
# Table 1 (Statistical Analysis)
career_amount_table <- pre_career_amount_table %>%
  bind_rows(post_career_amount_table) %>%
  rename(
    Type = test, 
    Min = min, 
    Median = median, 
    Mean = mean, 
    `Standard Dev` = std_dev, 
    Max = max
  )

career_amount_table %>%
  kbl(caption = "Comparing Statistical Summaries of Career Amounts") %>%
  kable_styling()

# Table 2 (0 and 10 Career Amount Analysis)
## Pre Test
pre_0_10_career_amount <- pre_entry_form_data %>%
  count(career_amount) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100
  ) %>%
  filter(career_amount == 0 | career_amount == 10) %>%
  mutate(test = "pre") %>%
  select(test, career_amount, proportion, percent)

## Post Test
post_0_10_career_amount <- post_entry_form_data %>%
  count(career_amount) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100
  ) %>%
  filter(career_amount == 0 | career_amount == 10) %>%
  mutate(test = "post") %>%
  select(test, career_amount, proportion, percent)

## Compare
career_amount_0_10_table <- pre_0_10_career_amount %>%
  bind_rows(post_0_10_career_amount) %>%
  rename(
    Type = test, 
    `Number of Careers` = career_amount, 
    Proportion = proportion, 
    Percent = percent
  )

career_amount_0_10_table %>%
  arrange(`Number of Careers`) %>%
  kbl(caption = "Comparing 0 and 10 Career Amounts") %>%
  kable_styling()
```

:::

## Most and Least Popular Careers

::: {.callout-note icon=false collapse="true"}
## Pre Test: Most and Least Common
::: {.callout-tip icon=false collapse="true"}
## Most Common Careers in the Pre-Test
```{r}
#| label: pre-most-career-cat

# Background
pre_entry_form_data_longer <- pre_entry_form_data %>%
  select(survey_type, career_one, career_two, career_three, career_four, career_five, career_six, career_seven, career_eight, career_nine, career_ten) %>% 
  pivot_longer(!survey_type, names_to = "career_num", values_to = "career") %>%
  select(-career_num) %>%
  filter(!is.na(career))

pre_career <- pre_entry_form_data_longer %>%
  count(career) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "pre"
  ) %>%
  select(test, career, n, proportion, percent) %>%
  rename(count = n)

# Most
pre_most_career <- pre_career %>%
  arrange(desc(count)) %>%
  head(10) %>%
  rename(
    Type = test, 
    Career = career, 
    Count = count, 
    Proportion = proportion, 
    Percent = percent
  ) %>%
  kbl(caption = "Most Common Career Chosen in Pre Test") %>%
  kable_styling()
pre_most_career
```

::: 

::: {.callout-tip icon=false collapse="true"}
## Least Common Careers in the Pre-Test
```{r}
#| label: pre-least-career-cat

# Least
pre_only_one <- pre_career %>%
  filter(count == "1") %>%
  pull(career)
cat("Careers that were chosen only once: ")
pre_only_one

pre_two_and_three <- pre_career %>%
  filter(count == 2 | count == 3) %>%
  arrange(count) %>%
  pull(career)
cat("Careers that were chosen only two or three times: ")
pre_two_and_three
```

:::

:::

::: {.callout-note icon=false collapse="true"}
## Post Test: Most and Least Common
::: {.callout-tip icon=false collapse="true"}
## Most Common Careers in the Post-Test
```{r}
#| label: post-most-career-cat

# Background
post_entry_form_data_longer <- post_entry_form_data %>%
  select(survey_type, career_one, career_two, career_three, career_four, career_five, career_six, career_seven, career_eight, career_nine, career_ten) %>% 
  pivot_longer(!survey_type, names_to = "career_num", values_to = "career") %>%
  select(-career_num) %>%
  filter(!is.na(career))

post_career <- post_entry_form_data_longer %>%
  count(career) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "post"
  ) %>%
  select(test, career, n, proportion, percent) %>%
  rename(count = n)

# Most
post_most_career <- post_career %>%
  arrange(desc(count)) %>%
  head(10) %>%
  rename(
    Type = test, 
    Career = career, 
    Count = count, 
    Proportion = proportion, 
    Percent = percent
  ) %>%
  kbl(caption = "Most Common Career Chosen in Post Test") %>%
  kable_styling()
post_most_career
```

::: 

::: {.callout-tip icon=false collapse="true"}
## Least Common Careers in the Post-Test
```{r}
#| label: post-least-career-cat

# Least
post_only_one <- post_career %>%
  filter(count == "1") %>%
  pull(career)
cat("Careers that were chosen only once: ")
post_only_one

post_two_and_three <- post_career %>%
  filter(count == 2 | count == 3) %>%
  arrange(count) %>%
  pull(career)
cat("Careers that were chosen only two or three times: ")
post_two_and_three
```

:::

::: 

::: {.callout-note icon=false collapse="true"}
## Difference Between Pre and Post-Test Career Choices
::: {.callout-tip icon=false collapse="true"}
## Change in Careers
```{r}
#| label: diff-careers

pre_diff_careers <- pre_career[!pre_career$career %in% post_career$career,] %>%
  pull(career)
cat("New careers present in the pre-test, but not post-test: ")
pre_diff_careers

post_new_careers <- post_career[!post_career$career %in% pre_career$career,] %>%
  pull(career)
cat("Careers present in the post-test, but not pre-test: ")
post_new_careers
```

:::

::: {.callout-tip icon=false collapse="true"}
## Constant Careers
```{r}
#| label: same-careers

same_careers <- post_career[post_career$career %in% pre_career$career,] %>%
  pull(career)
cat("The same careers present in both the pre and post-tests: ")
same_careers
```

:::

::: 

# Likert Scale Questions
## Question 1
**Question:** If I work hard to solve a problem, I'll find the answer. 

```{r}
#| label: work-hard

# Pre
pre_wh_order <- pre_entry_form_data %>%
  filter(!is.na(work_hard))

pre_wh_table <- pre_wh_order %>%
  count(work_hard) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "pre"
  )

# Post
post_wh_order <- post_entry_form_data %>%
  filter(!is.na(work_hard))

post_wh_table <- post_wh_order %>%
  count(work_hard) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "post"
  )

# Compare 
## Plot
percentage_data <- entry_form_data %>%
  filter(!is.na(work_hard)) %>% 
  group_by(survey_type, work_hard) %>%
  summarise(count = n()) %>%
  group_by(survey_type) %>%
  mutate(
    percentage = count / sum(count) * 100,
    survey_type = factor(survey_type, levels = c("Pre", "Post")))

one_wh_plot <- ggplot(data = percentage_data, mapping = aes(x = work_hard, y = percentage, fill = survey_type)) + 
  geom_col(position = 'dodge') + 
  geom_text(
    mapping = aes(x = work_hard, y = percentage, label = sprintf("%.2f%%", percentage)), 
    position = position_dodge(width = 0.9), 
    vjust = -0.5, 
    size = 3, 
    family = "Arial", 
    fontface = "bold"
  ) + 
  scale_fill_manual(
    name = "",
    labels = c("Pre Test", "Post Test"),
    values = colors 
  ) + 
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    x = "Student Responses", 
    y = "Percentage", 
    title = "I'll Find the Answer If I Work Hard", 
    subtitle = "WiSTEM 2023 - 2024"
  ) + 
  theme_minimal(base_family = "Arial") + 
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),  
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "top", 
    legend.text = element_text(size = 12), 
    axis.title = element_text(size = 12), 
    axis.text = element_text(size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

one_wh_plot
```

::: {.callout-note icon=false collapse="true"}
## Table for Work Hard
```{r}
## Table
wh_table_percent <- pre_wh_table %>%
  bind_rows(post_wh_table) %>%
  select(-n, -proportion) %>%
  pivot_wider(names_from = work_hard, values_from = percent) %>%
  kbl(caption = "Pre and Post Percent Distribution for work_hard") %>%
  kable_styling()
wh_table_percent
```

:::

## Question 2
**Question:** I am confident in my ability to apply prior knowledge to succeed in new projects. 

```{r}
#| label: knowledge

# Pre
pre_know_order <- pre_entry_form_data %>%
  filter(!is.na(knowledge))

pre_know_table <- pre_know_order %>%
  count(knowledge) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "pre"
  )

# Post
post_know_order <- post_entry_form_data %>%
  filter(!is.na(knowledge))

post_know_table <- post_know_order %>%
  count(knowledge) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "post"
  )

# Compare 
## Plot
percentage_data <- entry_form_data %>%
  filter(!is.na(knowledge)) %>% 
  group_by(survey_type, knowledge) %>%
  summarise(count = n()) %>%
  group_by(survey_type) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  mutate(
    percentage = count / sum(count) * 100,
    survey_type = factor(survey_type, levels = c("Pre", "Post")))

one_know_plot <- ggplot(data = percentage_data, mapping = aes(x = knowledge, y = percentage, fill = survey_type)) + 
  geom_col(position = 'dodge') + 
  geom_text(
    mapping = aes(x = knowledge, y = percentage, label = sprintf("%.2f%%", percentage)), 
    position = position_dodge(width = 0.9), 
    vjust = -0.5, 
    size = 3, 
    family = "Arial",  
    fontface = "bold"
  ) + 
  scale_fill_manual(
    name = "",
    labels = c("Pre Test", "Post Test"), 
    values = colors
  ) + 
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    x = "Student Responses", 
    y = "Percentage", 
    title = "Confident In Applying Prior Knowledge To New Projects", 
    subtitle = "WiSTEM 2023 - 2024"
  ) + 
  theme_minimal(base_family = "Arial") +  
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),  
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "top", 
    legend.text = element_text(size = 12), 
    axis.title = element_text(size = 12), 
    axis.text = element_text(size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
one_know_plot
```

::: {.callout-note icon=false collapse="true"}
## Table for Knowledge
```{r}
## Table
know_table_percent <- pre_know_table %>%
  bind_rows(post_know_table) %>%
  select(-n, -proportion) %>%
  pivot_wider(names_from = knowledge, values_from = percent) %>%
  kbl(caption = "Pre and Post Percent Distribution for knowledge") %>%
  kable_styling()
know_table_percent
```

:::

## Question 3
**Question:** I feel confident in my ability to do well in STE(A)M courses. 

```{r}
#| label: courses

# Pre
pre_course_order <- pre_entry_form_data %>%
  filter(!is.na(courses))

pre_course_table <- pre_course_order %>%
  count(courses) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "pre"
  )

# Post
post_course_order <- post_entry_form_data %>%
  filter(!is.na(courses))

post_course_table <- post_course_order %>%
  count(courses) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "post"
  )

# Compare
## Plot
percentage_data <- entry_form_data %>%
  filter(!is.na(courses)) %>% 
  group_by(survey_type, courses) %>%
  summarise(count = n()) %>%
  group_by(survey_type) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  mutate(
    percentage = count / sum(count) * 100,
    survey_type = factor(survey_type, levels = c("Pre", "Post")))

one_course_plot <- ggplot(data = percentage_data, mapping = aes(x = courses, y = percentage, fill = survey_type)) + 
  geom_col(position = 'dodge') + 
  geom_text(
    mapping = aes(x = courses, y = percentage, label = sprintf("%.2f%%", percentage)), 
    position = position_dodge(width = 0.9), 
    vjust = -0.5, 
    size = 3, 
    family = "Arial", 
    fontface = "bold"
  ) + 
  scale_fill_manual(
    name = "",
    labels = c("Pre Test", "Post Test"), 
    values = colors
  ) + 
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    x = "Student Responses", 
    y = "Percentage", 
    title = "Confident In Ability To Do Well In STE(A)M Courses", 
    subtitle = "WiSTEM 2023 - 2024"
  ) + 
  theme_minimal(base_family = "Arial") + 
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "top", 
    legend.text = element_text(size = 12), 
    axis.title = element_text(size = 12), 
    axis.text = element_text(size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

one_course_plot
```

::: {.callout-note icon=false collapse="true"}
## Table for Courses
```{r}
## Table
course_table_percent <- pre_course_table %>%
  bind_rows(post_course_table) %>%
  select(-n, -proportion) %>%
  pivot_wider(names_from = courses, values_from = percent) %>%
  kbl(caption = "Pre and Post Percent Distribution for courses") %>%
  kable_styling()
course_table_percent
```

:::

## Question 4
**Question:** I think I could be successful in a STE(A)M career. 

```{r}
#| label: succesful

# Pre
pre_succ_order <- pre_entry_form_data %>%
  filter(!is.na(succesful))

pre_succ_table <- pre_succ_order %>%
  count(succesful) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "pre"
  )

# Post
post_succ_order <- post_entry_form_data %>%
  filter(!is.na(succesful))

post_succ_table <- post_succ_order %>%
  count(succesful) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "post"
  )

# Compare
## Plot
percentage_data <- entry_form_data %>%
  filter(!is.na(succesful)) %>% 
  filter(!is.na(succesful)) %>%
  group_by(survey_type, succesful) %>%
  summarise(count = n()) %>%
  group_by(survey_type) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  mutate(
    percentage = count / sum(count) * 100,
    survey_type = factor(survey_type, levels = c("Pre", "Post")))

one_succ_plot <- ggplot(data = percentage_data, mapping = aes(x = succesful, y = percentage, fill = survey_type)) + 
  geom_col(position = 'dodge') + 
  geom_text(
    mapping = aes(x = succesful, y = percentage, label = sprintf("%.2f%%", percentage)), 
    position = position_dodge(width = 0.9), 
    vjust = -0.5, 
    size = 3, 
    family = "Arial", 
    fontface = "bold"
  ) + 
  scale_fill_manual(
    name = "",
    labels = c("Pre Test", "Post Test"), 
    values = colors
  ) + 
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    x = "Student Responses", 
    y = "Percentage", 
    title = "I Could Be Successful In A STE(A)M Career", 
    subtitle = "WiSTEM 2023 - 2024"
  ) + 
  theme_minimal(base_family = "Arial") + 
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "top", 
    legend.text = element_text(size = 12), 
    axis.title = element_text(size = 12), 
    axis.text = element_text(size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

one_succ_plot
```

::: {.callout-note icon=false collapse="true"}
## Table for Successful
```{r}
## Table
succ_table_percent <- pre_succ_table %>%
  bind_rows(post_succ_table) %>%
  select(-n, -proportion) %>%
  pivot_wider(names_from = succesful, values_from = percent) %>%
  kbl(caption = "Pre and Post Percent Distribution for succesful") %>%
  kable_styling()
succ_table_percent
```

:::

## Question 5
**Question:** People who work in a STE(A)M field can solve important problems. 

```{r}
#| label: important

# Pre
pre_imp_order <- pre_entry_form_data %>%
  filter(!is.na(important))

pre_imp_table <- pre_imp_order %>%
  count(important) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "pre"
  )

# Post
post_imp_order <- post_entry_form_data %>%
  filter(!is.na(important))

post_imp_table <- post_imp_order %>%
  count(important) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "post"
  )

# Compare
## Plot
percentage_data <- entry_form_data %>%
  filter(!is.na(important)) %>%
  group_by(survey_type, important) %>%
  summarise(count = n()) %>%
  group_by(survey_type) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  mutate(
    percentage = count / sum(count) * 100,
    survey_type = factor(survey_type, levels = c("Pre", "Post")))

one_imp_plot <- ggplot(data = percentage_data, mapping = aes(x = important, y = percentage, fill = survey_type)) + 
  geom_col(position = 'dodge') + 
  geom_text(
    mapping = aes(x = important, y = percentage, label = sprintf("%.2f%%", percentage)), 
    position = position_dodge(width = 0.9), 
    vjust = -0.5, 
    size = 3, 
    family = "Arial", 
    fontface = "bold"
  ) + 
  scale_fill_manual(
    name = "",
    labels = c("Pre Test", "Post Test"), 
    values = colors
  ) + 
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    x = "Student Responses", 
    y = "Percentage", 
    title = "People In The STE(A)M Field Solve Important Problems", 
    subtitle = "WiSTEM 2023 - 2024"
  ) + 
  theme_minimal(base_family = "Arial") + 
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "top", 
    legend.text = element_text(size = 12), 
    axis.title = element_text(size = 12), 
    axis.text = element_text(size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

one_imp_plot
```

::: {.callout-note icon=false collapse="true"}
## Table for Important
```{r}
## Table
imp_table_percent <- pre_imp_table %>%
  bind_rows(post_imp_table) %>%
  select(-n, -proportion) %>%
  pivot_wider(names_from = important, values_from = percent) %>%
  kbl(caption = "Pre and Post Percent Distribution for important") %>%
  kable_styling()
imp_table_percent
```

:::

## Question 6
**Question:** I am a member of a STE(A)M community. 

```{r}
#| label: member

# Pre
pre_mem_order <- pre_entry_form_data %>%
  filter(!is.na(member))

pre_mem_table <- pre_mem_order %>%
  count(member) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "pre"
  )

# Post
post_mem_order <- post_entry_form_data %>%
  filter(!is.na(member))

post_mem_table <- post_mem_order %>%
  count(member) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "post"
  )

# Compare 
## Plot
percentage_data <- entry_form_data %>%
  filter(!is.na(member)) %>%
  group_by(survey_type, member) %>%
  summarise(count = n()) %>%
  group_by(survey_type) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  mutate(
    percentage = count / sum(count) * 100,
    survey_type = factor(survey_type, levels = c("Pre", "Post")))

one_mem_plot <- ggplot(data = percentage_data, mapping = aes(x = member, y = percentage, fill = survey_type)) + 
  geom_col(position = 'dodge') + 
  geom_text(
    mapping = aes(x = member, y = percentage, label = sprintf("%.2f%%", percentage)), 
    position = position_dodge(width = 0.9), 
    vjust = -0.5, 
    size = 3, 
    family = "Arial",  # Change to your desired font
    fontface = "bold"
  ) + 
  scale_fill_manual(
    name = "",
    labels = c("Pre Test", "Post Test"), 
    values = colors  # Assuming 'colors' is defined elsewhere
  ) + 
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    x = "Student Responses", 
    y = "Percentage", 
    title = "I Am A Member Of A STE(A)M Community", 
    subtitle = "WiSTEM 2023 - 2024"
  ) + 
  theme_minimal(base_family = "Arial") +  # Set base font here
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position ="top", 
    legend.text = element_text(size = 12), 
    axis.title = element_text(size = 12), 
    axis.text = element_text(size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

one_mem_plot
```

::: {.callout-note icon=false collapse="true"}
## Table for Member
```{r}
## Table
mem_table_percent <- pre_mem_table %>%
  bind_rows(post_mem_table) %>%
  select(-n, -proportion) %>%
  pivot_wider(names_from = member, values_from = percent) %>%
  kbl(caption = "Pre and Post Percent Distribution for member") %>%
  kable_styling()
mem_table_percent
```

:::

## Question 7
**Question:** I think a career in STE(A)M may be a good fit for me. 

```{r}
#| label: career

# Pre 
pre_car_order <- pre_entry_form_data %>%
  filter(!is.na(career))

pre_car_table <- pre_car_order %>%
  count(career) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "pre"
  )

# Post
post_car_order <- post_entry_form_data %>%
  filter(!is.na(career))

post_car_table <- post_car_order %>%
  count(career) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "post"
  )

# Compare 
## Plot
percentage_data <- entry_form_data %>%
  filter(!is.na(career)) %>%
  group_by(survey_type, career) %>%
  summarise(count = n()) %>%
  group_by(survey_type) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  mutate(
    percentage = count / sum(count) * 100,
    survey_type = factor(survey_type, levels = c("Pre", "Post")))

one_car_plot <- ggplot(data = percentage_data, mapping = aes(x = career, y = percentage, fill = survey_type)) + 
  geom_col(position = 'dodge') + 
  geom_text(
    mapping = aes(x = career, y = percentage, label = sprintf("%.2f%%", percentage)), 
    position = position_dodge(width = 0.9), 
    vjust = -0.5, 
    size = 3, 
    family = "Arial", 
    fontface = "bold"
  ) + 
  scale_fill_manual(
    name = "",
    labels = c("Pre Test", "Post Test"), 
    values = colors
  ) + 
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    x = "Student Responses", 
    y = "Percentage", 
    title = "A Career In STE(A)M May Be A Good Fit For Me", 
    subtitle = "WiSTEM 2023 - 2024"
  ) + 
  theme_minimal(base_family = "Arial") + 
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "top", 
    legend.text = element_text(size = 12), 
    axis.title = element_text(size = 12), 
    axis.text = element_text(size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

one_car_plot
```

::: {.callout-note icon=false collapse="true"}
## Table for Career
```{r}
## Table
car_table_percent <- pre_car_table %>%
  bind_rows(post_car_table) %>%
  select(-n, -proportion) %>%
  pivot_wider(names_from = career, values_from = percent) %>%
  kbl(caption = "Pre and Post Percent Distribution for career") %>%
  kable_styling()
car_table_percent
```

:::

## Question 8
**Question:** “Future STE(A)M professional” as part of my identity is important to me. 

```{r}
#| label: identity

# Pre
pre_iden_order <- pre_entry_form_data %>%
  filter(!is.na(identity))

pre_iden_table <- pre_iden_order %>%
  count(identity) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "pre"
  )

# Post
post_iden_order <- post_entry_form_data %>%
  filter(!is.na(identity))

post_iden_table <- post_iden_order %>%
  count(identity) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "post"
  )

# Compare 
## Plot
percentage_data <- entry_form_data %>%
  filter(!is.na(identity)) %>%
  group_by(survey_type, identity) %>%
  summarise(count = n()) %>%
  group_by(survey_type) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  mutate(
    percentage = count / sum(count) * 100,
    survey_type = factor(survey_type, levels = c("Pre", "Post")))

one_iden_plot <- ggplot(data = percentage_data, mapping = aes(x = identity, y = percentage, fill = survey_type)) + 
  geom_col(position = 'dodge') + 
  geom_text(
    mapping = aes(x = identity, y = percentage, label = sprintf("%.2f%%", percentage)), 
    position = position_dodge(width = 0.9), 
    vjust = -0.5, 
    size = 3, 
    family = "Arial", 
    fontface = "bold"
  ) + 
  scale_fill_manual(
    name = "",
    labels = c("Pre Test", "Post Test"), 
    values = colors
  ) + 
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    x = "Student Responses", 
    y = "Percentage", 
    title = "'Future STE(A)M Professional' Is An Important Identity", 
    subtitle = "WiSTEM 2023 - 2024"
  ) + 
  theme_minimal(base_family = "Arial") + 
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "top", 
    legend.text = element_text(size = 12), 
    axis.title = element_text(size = 12), 
    axis.text = element_text(size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

one_iden_plot
```

::: {.callout-note icon=false collapse="true"}
## Table for Identity
```{r}
## Table
iden_table_percent <- pre_iden_table %>%
  bind_rows(post_iden_table) %>%
  select(-n, -proportion) %>%
  pivot_wider(names_from = identity, values_from = percent) %>%
  kbl(caption = "Pre and Post Percent Distribution for identity") %>%
  kable_styling()
iden_table_percent
```

:::

## Question 9
**Question:** If I entered a STE(A)M career, I could make a meaningful contribution to society. 
 
```{r}
#| label: meaningful

# Pre 
pre_mean_order <- pre_entry_form_data %>%
  filter(!is.na(meaningful))

pre_mean_table <- pre_mean_order %>%
  count(meaningful) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "pre"
  )

# Post 
post_mean_order <- post_entry_form_data %>%
  filter(!is.na(meaningful))

post_mean_table <- post_mean_order %>%
  count(meaningful) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "post"
  )

# Compare 
## Plot
percentage_data <- entry_form_data %>%
  filter(!is.na(meaningful)) %>%
  group_by(survey_type, meaningful) %>%
  summarise(count = n()) %>%
  group_by(survey_type) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  mutate(
    percentage = count / sum(count) * 100,
    survey_type = factor(survey_type, levels = c("Pre", "Post")))

one_mean_plot <- ggplot(data = percentage_data, mapping = aes(x = meaningful, y = percentage, fill = survey_type)) + 
  geom_col(position = 'dodge') + 
  geom_text(
    mapping = aes(x = meaningful, y = percentage, label = sprintf("%.2f%%", percentage)), 
    position = position_dodge(width = 0.9), 
    vjust = -0.5, 
    size = 3, 
    family = "Arial", 
    fontface = "bold"
  ) + 
  scale_fill_manual(
    name = "",
    labels = c("Pre Test", "Post Test"), 
    values = colors
  ) + 
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    x = "Student Responses", 
    y = "Percentage", 
    title = "I Could Make a Meaningful Contribution In STE(A)M", 
    subtitle = "WiSTEM 2023 - 2024"
  ) + 
  theme_minimal(base_family = "Arial") + 
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "top", 
    legend.text = element_text(size = 12), 
    axis.title = element_text(size = 12), 
    axis.text = element_text(size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

one_mean_plot
```

::: {.callout-note icon=false collapse="true"}
## Table for Meaningful
```{r}
## Table
mean_table_percent <- pre_mean_table %>%
  bind_rows(post_mean_table) %>%
  select(-n, -proportion) %>%
  pivot_wider(names_from = meaningful, values_from = percent) %>%
  kbl(caption = "Pre and Post Percent Distribution for meaningful") %>%
  kable_styling()
mean_table_percent
```

:::
## Question 10
**Question:** I understand what everyday STE(A)M work is like. 

```{r}
#| label: everyday

# Pre 
pre_every_order <- pre_entry_form_data %>%
  filter(!is.na(everyday))

pre_every_table <- pre_every_order %>%
  count(everyday) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "pre"
  )

# Post
post_every_order <- post_entry_form_data %>%
  filter(!is.na(everyday))

post_every_table <- post_every_order %>%
  count(everyday) %>%
  mutate(
    proportion = n / sum(n), 
    percent = proportion * 100, 
    test = "post"
  )

# Compare 
## Plot
percentage_data <- entry_form_data %>%
  filter(!is.na(everyday)) %>%
  group_by(survey_type, everyday) %>%
  summarise(count = n()) %>%
  group_by(survey_type) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  mutate(
    percentage = count / sum(count) * 100,
    survey_type = factor(survey_type, levels = c("Pre", "Post")))

one_every_plot <- ggplot(data = percentage_data, mapping = aes(x = everyday, y = percentage, fill = survey_type)) + 
  geom_col(position = 'dodge') + 
  geom_text(
    mapping = aes(x = everyday, y = percentage, label = sprintf("%.2f%%", percentage)), 
    position = position_dodge(width = 0.9), 
    vjust = -0.5, 
    size = 3, 
    family = "Arial", 
    fontface = "bold"
  ) + 
  scale_fill_manual(
    name = "",
    labels = c("Pre Test", "Post Test"), 
    values = colors
  ) + 
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    x = "Student Responses", 
    y = "Percentage", 
    title = "I Understand What Everyday STE(A)M Work Is Like", 
    subtitle = "WiSTEM 2023 - 2024"
  ) + 
  theme_minimal(base_family = "Arial") + 
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "top", 
    legend.text = element_text(size = 12), 
    axis.title = element_text(size = 12), 
    axis.text = element_text(size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
one_every_plot
```

::: {.callout-note icon=false collapse="true"}
## Table for Everyday
```{r}
## Table
every_table_percent <- pre_every_table %>%
  bind_rows(post_every_table) %>%
  select(-n, -proportion) %>%
  pivot_wider(names_from = everyday, values_from = percent) %>%
  kbl(caption = "Pre and Post Percent Distribution for everyday") %>%
  kable_styling()
every_table_percent
```

:::
