---
title: "WiSTEM 2023 - 2024"
subtitle: "Exit Slip Analysis"
format:
  html:
    toc: true
    embed-resources: true
    echo: false
    link-external-newwindow: true
execute:
  warning: false
  message: false
from: markdown+emoji  
editor: 
  markdown: 
    wrap: 72
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: load-packages

library(tidyverse)
library(patchwork)
library(readr)
library(kableExtra)

set.seed(1968)
```

```{r}
#| label: load-data-set

# Load Data
wistem_exit_slip_data <- read_csv(file = "data/processed/wistem_2324_exit_slips_processed.csv")
wistem_attendance_data <- read_csv(file = "data/processed/wistem_2324_attendance_processed.csv")

# Leveling
wistem_exit_slip_data$interesting <- factor(wistem_exit_slip_data$interesting, levels = c("Somewhat", "Fairly", "Very"))
wistem_exit_slip_data$included <- factor(wistem_exit_slip_data$included, levels = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))
wistem_exit_slip_data$belong <- factor(wistem_exit_slip_data$belong, levels = c("Strongly disagree", "Neutral", "Agree", "Strongly agree"))

wistem_exit_slip_data$date <- factor(wistem_exit_slip_data$date, levels = c("Sep 29th", "Oct 13th", "Oct 27th", "Nov 17th", "Dec 1st", "Dec 15th", "Jan 18th", "Jan 19th", "Feb 16th", "Mar 1st", "Mar 15th", "Apr 5th", "Apr 19th", "May 3rd"))

wistem_attendance_data$date <- factor(wistem_attendance_data$date, levels = c("Sep 29th", "Oct 13th", "Oct 27th", "Nov 15th", "Nov 17th", "Dec 1st", "Dec 15th", "Jan 18th", "Mar 1st", "Mar 15th", "Apr 5th", "Apr 19th", "May 6th"))

# Colors
color <- c("#716C6B")
fill <- c("#B6ACD1")
```

# Background

**WiSTEM:** In total, there were 15 overall WiSTEM meetings held throughout the 2023-2024 academic school year. There were 14 meetings with attendance data and 14 meetings with exit slip data. There is an overlap in the meeting missing both attendance and exit slip data.

**Exit Slips Distribution:** Overall, there were 483 total exit slips collected over the course of the 2023-2024 academic school year. The graph and table below show the number of exit slips obtained for each of the 14 meetings where exit slips were provided: 
```{r}
#| label: exit-slip-per-meeting

# Graph
ggplot(data = wistem_exit_slip_data, mapping = aes(y = date)) +
  geom_bar(color = color, fill = fill) + 
  geom_text(
    stat = 'count', 
    mapping = aes(label = ..count..), 
    position = position_stack(vjust = 0.9),
    family = "Georgia", 
    fontface = "bold"
    ) +
  labs(
    title = "Number of Exit Slips Per Meeting", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responsesz", 
    y = "Meeting Date"
    ) +
  theme_minimal() + 
  theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Table for Number of Exit Slips Per Meeting
```{r}
# Table
wistem_exit_slip_data %>%
  filter(!is.na(date)) %>%
  count(date) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  rename(count = n) %>%
  kbl(caption = "Number of Exit Slips Per Meeting") %>%
  kable_styling()
```

:::

# Completion Rate

```{r}
#| label: completion

# Creating Data
attendance_completion <- wistem_attendance_data %>%
  filter(!is.na(date)) %>% 
  count(date) %>% 
  rename(count = n) %>% 
  mutate(type = "attendance")

exit_completion <- wistem_exit_slip_data %>% 
  filter(!is.na(date)) %>% 
  count(date) %>% 
  rename(count = n) %>% 
  mutate(type = "exit slips")

completion_data <- rbind(attendance_completion, exit_completion)

completion_data <- pivot_wider(completion_data, names_from = type, values_from = count) 

completion_data <- completion_data %>% 
  mutate(
    completion_prop = `exit slips` / attendance, 
    completion_percent = completion_prop * 100
    ) %>%
  rename(
    Date = date, 
    `Exit Slip Count` = `exit slips`, 
    `Attendance Count` = attendance, 
    Proportion = completion_prop, 
    Percent = completion_percent
  ) %>% 
  select(Date, `Exit Slip Count`, `Attendance Count`, Proportion, Percent)

# Leveling
completion_data$Date <- factor(completion_data$Date, levels = c("Sep 29th", "Oct 13th", "Oct 27th", "Nov 15th", "Nov 17th", "Dec 1st", "Dec 15th", "Jan 18th", "Jan 19th", "Feb 16th", "Mar 1st", "Mar 15th", "Apr 5th", "Apr 19th", "May 3rd", "May 6th"))

completion_data %>%
  kbl(caption = "Exit Slip Completion Rate Per Meeting") %>%
  kable_styling()
```

# Overall Distribution Per Category
## Question 1
**Question:** How interesting was today's meeting?

```{r}
#| label: avg-interesting

# Graph
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(interesting)) %>% 
  group_by(interesting) %>%
  summarize(percentage = n() / nrow(wistem_exit_slip_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "Overall", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Table for Overall Interesting
```{r}
# Table
wistem_exit_slip_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```
:::

## Question 2
**Question:** I feel included in WiSTEM. 

```{r}
#| label: avg-included

# Graph
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(included)) %>% 
  group_by(included) %>%
  summarize(percentage = n() / nrow(wistem_exit_slip_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I Feel Included in WiSTEM", 
    subtitle = "Overall", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Table for Overall Included
```{r}
# Table
wistem_exit_slip_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Included") %>%
  kable_styling()
```
:::

## Question 3
**Question:** I belong in a STE(A)M community. 

```{r}
#| label: avg-belong

# Graph
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(belong)) %>% 
  group_by(belong) %>%
  summarize(percentage = n() / nrow(wistem_exit_slip_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "Overall", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Table for Overall Belong
```{r}
# Table
wistem_exit_slip_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Belong") %>%
  kable_styling()
```
:::

# Distribution Per Meeting

## September 29th, 2023
**Topic:** Activity

```{r}
#| label: sep-29-2023

# Interesting
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Sep 29th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "September 29th, 2023", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Sep 29th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in WiSTEM", 
    subtitle = "September 29th, 2023", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Sep 29th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "September 29th, 2023", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for September 29th, 2023

```{r}
# Interesting
wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Sep 29th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Sep 29th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Sep 29th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## October 13th, 2023
**Topic:** Activity

```{r}
#| label: oct-13-2023

# Interesting
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Oct 13th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "October 13th, 2023", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Oct 13th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in WiSTEM", 
    subtitle = "October 13th, 2023", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Oct 13th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "October 13th, 2023", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for October 13th, 2023

```{r}
# Interesting
wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Oct 13th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Oct 13th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Oct 13th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## October 27th, 2023
**Topic:** Activity

```{r}
#| label: oct-27-2023

# Interesting
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Oct 27th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "October 27th, 2023", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Oct 27th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in WiSTEM", 
    subtitle = "October 27th, 2023", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Oct 27th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "October 27th, 2023", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for October 27th, 2023

```{r}
# Interesting
wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Oct 27th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Oct 27th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Oct 27th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## November 17th, 2023
**Topic:** Guest Presenter

```{r}
#| label: nov-17-2023

# Interesting
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Nov 17th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "November 17th, 2023", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Nov 17th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in WiSTEM", 
    subtitle = "November 17th, 2023", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Nov 17th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "November 17th, 2023", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for November 17th, 2023

```{r}
# Interesting
wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Nov 17th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Nov 17th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Nov 17th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## December 1st, 2023
**Topic:** Discussion

```{r}
#| label: dec-01-2023

# Interesting
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Dec 1st") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "December 1st, 2023", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Dec 1st") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in WiSTEM", 
    subtitle = "December 1st, 2023", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Dec 1st") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "December 1st, 2023", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for December 1st, 2023

```{r}
# Interesting
wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Dec 1st") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Dec 1st") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Dec 1st") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## December 15th, 2023
**Topic:** Hangout

```{r}
#| label: dec-15-2023

# Interesting
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Dec 15th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "December 15th, 2023", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Dec 15th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in WiSTEM", 
    subtitle = "December 15th, 2023", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Dec 15th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "December 15th, 2023", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for December 15th, 2023

```{r}
# Interesting
wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Dec 15th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Dec 15th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Dec 15th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## January 18th, 2024
**Topic:** Out of School Event

```{r}
#| label: jan-18-2024

# Interesting
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Jan 18th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "January 18th, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Jan 18th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in WiSTEM", 
    subtitle = "January 18th, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Jan 18th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "January 18th, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for January 18th, 2024

```{r}
# Interesting
wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Jan 18th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Jan 18th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Jan 18th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## January 19th, 2024
**Topic:** Guest Presenter

```{r}
#| label: jan-19-2024

# Interesting
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Jan 19th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "January 19th, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Jan 19th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in WiSTEM", 
    subtitle = "January 19th, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Jan 19th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "January 19th, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for January 19th, 2024

```{r}
# Interesting
wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Jan 19th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Jan 19th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Jan 19th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## February 16th, 2024
**Topic:** Guest Speaker

```{r}
#| label: feb-16-2023

# Interesting
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Feb 16th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "February 16th, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Feb 16th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in WiSTEM", 
    subtitle = "February 16th, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Feb 16th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "February 16th, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for February 16th, 2024

```{r}
# Interesting
wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Feb 16th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Feb 16th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Feb 16th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## March 1st, 2024
**Topic:** Activity

```{r}
#| label: mar-01-2024

# Interesting
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Mar 1st") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "March 1st, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Mar 1st") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in WiSTEM", 
    subtitle = "March 1st, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Mar 1st") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "March 1st, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for March 1st, 2024

```{r}
# Interesting
wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Mar 1st") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Mar 1st") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Mar 1st") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## March 15th, 2024
**Topic:** Activity

```{r}
#| label: mar-15-2024

# Interesting
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Mar 15th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "March 15th, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Mar 15th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in WiSTEM", 
    subtitle = "March 15th, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Mar 15th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "March 15th, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for March 15th, 2024

```{r}
# Interesting
wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Mar 15th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Mar 15th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Mar 15th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## April 5th, 2024
**Topic:** Guest Presenter

```{r}
#| label: apr-05-2023

# Interesting
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Apr 5th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "April 5th, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Apr 5th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in WiSTEM", 
    subtitle = "April 5th, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Apr 5th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "April 5th, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for April 5th, 2024

```{r}
# Interesting
wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Apr 5th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Apr 5th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Apr 5th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## April 19th, 2024
**Topic:** Activity

```{r}
#| label: apr-19-2024

# Interesting
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Apr 19th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "April 19th, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Apr 19th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in WiSTEM", 
    subtitle = "April 19th, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Apr 19th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "April 19th, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for April 19th, 2024

```{r}
# Interesting
wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "Apr 19th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wistem_exit_slip_data %>%
  filter(!is.na(included), date == "Apr 19th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "Apr 19th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## May 3rd, 2024
**Topic:** Activity

```{r}
#| label: may-03-2024

# Interesting
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "May 3rd") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "May 3rd, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(included), date == "May 3rd") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in WiSTEM", 
    subtitle = "May 3rd, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "May 3rd") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "May 3rd, 2024", 
    caption = "Source: WiSTEM 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for May 3rd, 2024

```{r}
# Interesting
wistem_exit_slip_data %>%
  filter(!is.na(interesting), date == "May 3rd") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wistem_exit_slip_data %>%
  filter(!is.na(included), date == "May 3rd") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wistem_exit_slip_data %>%
  filter(!is.na(belong), date == "May 3rd") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::
