---
title: "WiSTEM 2023 - 2024"
subtitle: "Attendance Analysis"
format:
  html:
    toc: true
    embed-resources: true
    echo: false
    link-external-newwindow: true
execute:
  warning: false
  message: false
from: markdown+emoji  
editor: 
  markdown: 
    wrap: 72
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: load-packages

library(tidyverse)
library(patchwork)
library(readr)
library(kableExtra)

set.seed(1968)
```

```{r}
#| label: load-data-set

# Load Data
wieng_attendance_data <- read_csv(file = "data/processed/wieng_2324_attendance_processed.csv")

# Leveling
wieng_attendance_data$date <- factor(wieng_attendance_data$date, levels = c("Oct 6th", "Oct 13th", "Oct 20th", "Nov 3rd", "Nov 17th", "Dec 1st", "Dec 8th", "Dec 15th", "Dec 16th", "Jan 19th", "Jan 26th", "Feb 2nd", "Feb 9th", "Feb 16th", "Feb 23rd", "Mar 1st", "Mar 8th", "Mar 15th", "Mar 22nd", "Apr 5th", "Apr 12th", "Apr 19th", "Apr 26th", "May 3rd", "May 10th", "May 17th"))

# Colors
color <- c("#716C6B")
fill <- c("#B6ACD1")

unique_colors <- c("lavender", "darkseagreen2", "lightpink2", "khaki", "lightcyan2", "peachpuff")
```

# Background

**WiENG:** In total, there were 27 overall WiENG meetings held throughout the 2023-2024 academic school year. However, there were 27 meetings with attendance data and 23 meetings with exit slip data. Some of these overlap in missing both attendance and exit slip data.

**Exit Slips Distribution:** Overall, there were 303 total exit slips collected over the course of the 2023-2024 academic school year. The graph and table below show the number of exit slips obtained for each of the 23 meetings where exit slips were provided.

