---
title: "WiENG 2023 - 2024"
subtitle: "Exit Slip Analysis"
format:
  html:
    toc: true
    embed-resources: true
    echo: false
    link-external-newwindow: true
execute:
  warning: false
  message: false
from: markdown+emoji  
editor: 
  markdown: 
    wrap: 72
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: load-packages

library(tidyverse)
library(patchwork)
library(readr)
library(kableExtra)

set.seed(1968)
```

```{r}
#| label: load-data-set

# Load Data
wieng_exit_slip_data <- read_csv(file = "data/processed/wieng_2324_exit_slips_processed.csv")
wieng_attendance_data <- read_csv(file = "data/processed/wieng_2324_attendance_processed.csv")

# Leveling
wieng_exit_slip_data$interesting <- factor(wieng_exit_slip_data$interesting, levels = c("Somewhat", "Fairly", "Very"))
wieng_exit_slip_data$included <- factor(wieng_exit_slip_data$included, levels = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))
wieng_exit_slip_data$belong <- factor(wieng_exit_slip_data$belong, levels = c("Strongly disagree", "Neutral", "Agree", "Strongly agree"))

wieng_exit_slip_data$date <- factor(wieng_exit_slip_data$date, levels = c("Oct 6th", "Oct 13th", "Oct 20th", "Nov 3rd", "Nov 17th", "Dec 1st", "Dec 8th", "Dec 15th", "Jan 19th", "Jan 26th", "Feb 2nd", "Feb 9th", "Feb 16th", "Feb 23rd", "Mar 1st", "Mar 8th", "Mar 15th", "Mar 22nd", "Apr 5th", "Apr 12th", "Apr 19th", "Apr 26th", "May 3rd", "May 10th", "May 17th"))

wieng_attendance_data$date <- factor(wieng_attendance_data$date, levels = c("Oct 6th", "Oct 13th", "Oct 20th", "Nov 3rd", "Nov 17th", "Dec 1st", "Dec 8th", "Dec 15th", "Dec 16th", "Jan 19th", "Jan 26th", "Feb 2nd", "Feb 9th", "Feb 16th", "Feb 23rd", "Mar 1st", "Mar 8th", "Mar 15th", "Mar 22nd", "Apr 5th", "Apr 12th", "Apr 19th", "Apr 26th", "May 3rd", "May 10th", "May 17th"))

# Colors
color <- c("#716C6B")
fill <- c("#B6ACD1")
```

# Background

**WiENG:** In total, there were 27 overall WiENG meetings held throughout the 2023-2024 academic school year. However, there were 27 meetings with attendance data and 23 meetings with exit slip data. Some of these overlap in missing both attendance and exit slip data.

**Exit Slips Distribution:** Overall, there were 303 total exit slips collected over the course of the 2023-2024 academic school year. The graph and table below show the number of exit slips obtained for each of the 23 meetings where exit slips were provided: 
```{r}
#| label: exit-slip-per-meeting

# Graph
ggplot(data = wieng_exit_slip_data, mapping = aes(y = date)) +
  geom_bar(color = color, fill = fill) + 
  geom_text(
    stat = 'count', 
    mapping = aes(label = ..count..), 
    position = position_stack(vjust = 0.9),
    family = "Georgia", 
    fontface = "bold"
    ) +
  labs(
    title = "Number of Exit Slips Per Meeting", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responsesz", 
    y = "Meeting Date"
    ) +
  theme_minimal() + 
  theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Table for Number of Exit Slips Per Meeting
```{r}
# Table
wieng_exit_slip_data %>%
  filter(!is.na(date)) %>%
  count(date) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  rename(count = n) %>%
  kbl(caption = "Number of Exit Slips Per Meeting") %>%
  kable_styling()
```

:::

# Completion Rate

```{r}
#| label: completion

# Creating Data
attendance_completion <- wieng_attendance_data %>%
  filter(!is.na(date)) %>% 
  count(date) %>% 
  rename(count = n) %>% 
  mutate(type = "attendance")

exit_completion <- wieng_exit_slip_data %>% 
  filter(!is.na(date)) %>% 
  count(date) %>% 
  rename(count = n) %>% 
  mutate(type = "exit slips")

completion_data <- rbind(attendance_completion, exit_completion)

completion_data <- pivot_wider(completion_data, names_from = type, values_from = count) 

completion_data <- completion_data %>% 
  mutate(
    completion_prop = `exit slips` / attendance, 
    completion_percent = completion_prop * 100
    ) %>%
  rename(
    Date = date, 
    `Exit Slip Count` = `exit slips`, 
    `Attendance Count` = attendance, 
    Proportion = completion_prop, 
    Percent = completion_percent
  ) %>% 
  select(Date, `Exit Slip Count`, `Attendance Count`, Proportion, Percent)

# Leveling
completion_data$Date <- factor(completion_data$Date, levels = c("Oct 6th", "Oct 13th", "Oct 20th", "Nov 3rd", "Nov 17th", "Dec 1st", "Dec 5th", "Dec 8th", "Dec 15th", "Dec 16th", "Jan 19th", "Jan 26th", "Feb 2nd", "Feb 9th", "Feb 16th", "Feb 23rd", "Mar 1st", "Mar 8th", "Mar 15th", "Mar 22nd", "Apr 5th", "Apr 12th", "Apr 19th", "Apr 26th", "May 3rd", "May 10th", "May 17th"))

completion_data %>%
  kbl(caption = "Exit Slip Completion Rate Per Meeting") %>%
  kable_styling()
```

# Overall Distribution Per Category
## Question 1
**Question:** How interesting was today's meeting?

```{r}
#| label: avg-interesting

# Graph
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting)) %>% 
  group_by(interesting) %>%
  summarize(percentage = n() / nrow(wieng_exit_slip_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "Overall", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Table for Overall Interesting
```{r}
# Table
wieng_exit_slip_data %>%
  filter(!is.na(interesting)) %>%
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```
:::

## Question 2
**Question:** I feel included in wieng. 

```{r}
#| label: avg-included

# Graph
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included)) %>% 
  group_by(included) %>%
  summarize(percentage = n() / nrow(wieng_exit_slip_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I Feel Included in wieng", 
    subtitle = "Overall", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Table for Overall Included
```{r}
# Table
wieng_exit_slip_data %>%
  filter(!is.na(included)) %>%
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Included") %>%
  kable_styling()
```
:::

## Question 3
**Question:** I belong in a STE(A)M community. 

```{r}
#| label: avg-belong

# Graph
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong)) %>% 
  group_by(belong) %>%
  summarize(percentage = n() / nrow(wieng_exit_slip_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "Overall", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Table for Overall Belong
```{r}
# Table
wieng_exit_slip_data %>%
  filter(!is.na(belong)) %>%
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Belong") %>%
  kable_styling()
```
:::

# Distribution Per Meeting

## October 6th, 2023
**Topic:** Activity

```{r}
#| label: oct-06-2023

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Oct 6th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "October 6th, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Oct 6th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "October 6th, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Oct 6th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "October 6th, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for October 6th, 2023

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Oct 6th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Oct 6th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Oct 6th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## October 13th, 2023
**Topic:** Activity

```{r}
#| label: oct-13-2023

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Oct 13th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "October 13th, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Oct 13th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "October 13th, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Oct 13th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "October 13th, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for October 13th, 2023

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Oct 13th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Oct 13th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Oct 13th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## October 20th, 2023
**Topic:** Activity

```{r}
#| label: oct-20-2023

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Oct 20th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "October 20th, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Oct 20th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "October 20th, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Oct 20th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "October 20th, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for October 20th, 2023

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Oct 20th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Oct 20th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Oct 20th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## November 3rd, 2023
**Topic:** Activity

```{r}
#| label: nov-03-2023

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Nov 3rd") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "November 3rd, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Nov 3rd") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "November 3rd, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Nov 3rd") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "November 3rd, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for November 3rd, 2023

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Nov 3rd") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Nov 3rd") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Nov 3rd") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## November 17th, 2023
**Topic:** Activity

```{r}
#| label: nov-17-2023

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Nov 17th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "November 17th, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Nov 17th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "November 17th, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Nov 17th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "November 17th, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for November 17th, 2023

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Nov 17th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Nov 17th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Nov 17th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## December 1st, 2023
**Topic:** Activity

```{r}
#| label: dec-01-2023

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Dec 1st") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "December 1st, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Dec 1st") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "December 1st, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Dec 1st") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "December 1st, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for December 1st, 2023

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Dec 1st") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Dec 1st") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Dec 1st") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## December 8th, 2023
**Topic:** Discussion

```{r}
#| label: dec-08-2023

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Dec 8th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "December 8th, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Dec 8th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "December 8th, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Dec 8th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "December 8th, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for December 8th, 2023

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Dec 8th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Dec 8th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Dec 8th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## December 15th, 2023
**Topic:** Activity

```{r}
#| label: dec-15-2023

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Dec 15th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "December 15th, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Dec 15th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "December 15th, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Dec 15th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "December 15th, 2023", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for December 15th, 2023

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Dec 15th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Dec 15th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Dec 15th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## January 19th, 2024
**Topic:** Activity

```{r}
#| label: jan-19-2024

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Jan 19th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "January 19th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Jan 19th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "January 19th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Jan 19th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "January 19th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for January 19th, 2024

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Jan 19th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Jan 19th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Jan 19th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## January 26th, 2024
**Topic:** Activity

```{r}
#| label: jan-26-2024

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Jan 26th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "January 26th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Jan 26th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "January 26th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Jan 26th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "January 26th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for January 26th, 2024

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Jan 26th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Jan 26th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Jan 26th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## February 2nd, 2024
**Topic:** Activity

```{r}
#| label: feb-02-2024

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Feb 2nd") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "February 2nd, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Feb 2nd") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "February 2nd, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Feb 2nd") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "February 2nd, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for February 2nd, 2024

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Feb 2nd") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Feb 2nd") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Feb 2nd") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## February 16th, 2024
**Topic:** Activity

```{r}
#| label: feb-16-2024

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Feb 16th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "February 16th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Feb 16th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "February 16th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Feb 16th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "February 16th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for February 16th, 2024

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Feb 16th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Feb 16th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Feb 16th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## February 23rd, 2024
**Topic:** Activity

```{r}
#| label: feb-23-2024

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Feb 23rd") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "February 23rd, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Feb 23rd") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "February 23rd, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Feb 23rd") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "February 23rd, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for February 23rd, 2024

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Feb 23rd") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Feb 23rd") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Feb 23rd") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## March 1st, 2024
**Topic:** Activity

```{r}
#| label: mar-01-2024

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Mar 1st") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "March 1st, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Mar 1st") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "March 1st, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Mar 1st") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "March 1st, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for March 1st, 2024

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Mar 1st") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Mar 1st") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Mar 1st") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## March 8th, 2024
**Topic:** Activity

```{r}
#| label: mar-08-2024

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Mar 8th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "March 8th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Mar 8th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "March 8th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Mar 8th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "March 8th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for March 8th, 2024

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Mar 8th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Mar 8th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Mar 8th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## March 15th, 2024
**Topic:** Activity

```{r}
#| label: mar-15-2024

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Mar 15th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "March 15th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Mar 15th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "March 15th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Mar 15th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "March 15th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for March 15th, 2024

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Mar 15th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Mar 15th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Mar 15th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## March 22nd, 2024
**Topic:** Activity

```{r}
#| label: mar-22-2024

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Mar 22nd") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "March 22nd, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Mar 22nd") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "March 22nd, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Mar 22nd") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "March 22nd, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for March 22nd, 2024

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Mar 22nd") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Mar 22nd") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Mar 22nd") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## April 5th, 2024
**Topic:** Activity

```{r}
#| label: apr-05-2024

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Apr 5th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "April 5th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Apr 5th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "April 5th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Apr 5th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "April 5th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for April 5th, 2024

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Apr 5th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Apr 5th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Apr 5th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## April 12th, 2024
**Topic:** Guest Presenter

```{r}
#| label: apr-12-2024

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Apr 12th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "April 12th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Apr 12th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "April 12th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Apr 12th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "April 12th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for April 12th, 2024

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Apr 12th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Apr 12th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Apr 12th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## April 19th, 2024
**Topic:** Activity

```{r}
#| label: apr-19-2024

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Apr 19th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "April 19th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Apr 19th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "April 19th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Apr 19th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "April 19th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for April 19th, 2024

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Apr 19th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Apr 19th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Apr 19th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## April 26th, 2024
**Topic:** Guest Presenter

```{r}
#| label: apr-26-2024

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Apr 26th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "April 26th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Apr 26th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "April 26th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Apr 26th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "April 26th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for April 26th, 2024

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "Apr 26th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "Apr 26th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "Apr 26th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## May 3rd, 2024
**Topic:** Activity

```{r}
#| label: may-03-2024

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "May 3rd") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "May 3rd, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "May 3rd") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "May 3rd, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "May 3rd") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "May 3rd, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for May 3rd, 2024

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "May 3rd") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "May 3rd") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "May 3rd") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## May 10th, 2024
**Topic:** Hangout

```{r}
#| label: may-10-2024

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "May 10th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "May 10th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "May 10th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "May 10th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "May 10th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "May 10th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for May 10th, 2024

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "May 10th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "May 10th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "May 10th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

## May 17th, 2024
**Topic:** Activity

```{r}
#| label: may-17-2024

# Interesting
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "May 17th") %>% 
  group_by(interesting) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = interesting, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = interesting, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "How Interesting Was Today’s Meeting?", 
    subtitle = "May 17th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Included
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(included), date == "May 17th") %>% 
  group_by(included) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = included, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = included, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I feel included in wieng", 
    subtitle = "May 17th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

# Belong
percentage_data <- wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "May 17th") %>% 
  group_by(belong) 

percentage_data <- percentage_data %>%
  summarize(percentage = n() / nrow(percentage_data) * 100)

ggplot(data = percentage_data, mapping = aes(x = belong, y = percentage)) + 
  geom_col(color = color, fill = fill) + 
  geom_text(
    data = percentage_data, 
    mapping = aes(x = belong, y = percentage, label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, 
    family = "Georgia", 
    fontface = "bold"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  labs(
    title = "I belong in a STE(A)M community", 
    subtitle = "May 17th, 2024", 
    caption = "Source: WiENG 2023-2024",
    x = "Number of Responses", 
    y = "Count"
    ) +
  theme_minimal() + 
    theme(
    plot.title = element_text(hjust = 0.5, family = "Georgia", face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, family = "Georgia"),
    legend.position ="top", 
    legend.text = element_text(family = "Georgia", size = 12), 
    axis.title = element_text(family = "Georgia", size = 12), 
    axis.text = element_text(family = "Georgia", size = 10), 
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
```

::: {.callout-note icon=false collapse="true"}
## Tables for May 17th, 2024

```{r}
# Interesting
wieng_exit_slip_data %>%
  filter(!is.na(interesting), date == "May 17th") %>% 
  count(interesting) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Included
wieng_exit_slip_data %>%
  filter(!is.na(included), date == "May 17th") %>% 
  count(included) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()

# Belong
wieng_exit_slip_data %>%
  filter(!is.na(belong), date == "May 17th") %>% 
  count(belong) %>%
  mutate(
    proportion = n / sum(n), 
    percent = (n / sum(n)) * 100 
  ) %>%
  arrange(desc(n)) %>%
  rename(count = n) %>%
  kbl(caption = "Distribution for Interesting") %>%
  kable_styling()
```

:::

